\section{Attach Handles}
\label{section:pl-handle}

At this point in the chapter we have constructed a 4--manifold triangulation $W$ with two boundary components, each equivalent via subdivision to the 3--dimensional cell complex $M$ obtained in Section \ref{section:pl-subdivide}.
Furthermore, the simplices of $M$ are partitioned into subtriangulations analogous to the face, edge, and vertex blocks of Chapter \ref{chapter:smooth}.
Explicit attachment sites are available for (4,2)--handles, so our first step is construction of a (4,2)--handle.

\subsection{2--handles}
\label{section:pl-2-handle}

The algorithm of this subsection takes as input a pair $(T,\Gamma)$ where $T$ is a closed solid torus triangulation and $\Gamma$ is a collection disjoint parallel longitudes in the boundary of $T$, given as subtriangulations of $\pd T$.
The output is a 4--disk triangulation $H$ satisfying the following:
\begin{enumerate}
	\item $\pd H$ is a triangulated $S^3$ with a genus 1 Heegard splitting over $\pd T$, i.e.\ $T$ is a subtriangulation of $\pd H$ such that $\pd H\setminus \interior{T}$ is a solid torus.
	\item For each $\gamma_i$ in $\Gamma$, $\gamma_i$ bounds a triangulated disk in $\pd H$, i.e.\ each $\gamma_i$ is an explicit 0-framing for the (4,2)--handle attachment.
\end{enumerate}
We take $H$ to be a (4,2)--handle and attach $H$ to $W$ over $T$.
Constructing the handle involves building a solid torus $T'$ that complements $T$, combining $T$ and $T'$ over their shared boundary to build a triangulated 3--sphere, then coning that 3--sphere into the 4--disk $H$.

We find pairs $(T,\Gamma)$ inside $M_1\subset\pd W$, the subdivision of $N$ induced by the subdividing map $f:N\to\RR$.
Let $B$ be a combinatorial face block of $M_1$.
$B$ is a 3--dimensional subtriangulation of $M_1$ that forms a closed solid torus,
% Prove?
and $B$ projects through $f$ over an $n$--gon for some $n$.
Call the $n$ corners of $f(B)$ by $c_i$, $i=1\dots n$, and take $C=\{c_1\dots c_n\}$.
Then the $f\inv c_i$ are disjoint parallel triangulated longitudes of $B$.
We take $(B, f\inv C)$ as our pair $(T,\Gamma)$ for each combinatorial face block $B$ of $M$.

For a closed solid torus $T$, we find a complementary torus $T'$, i.e.\ $\pd T=\pd T'$ as triangulations.
We begin by investigating the boundary of $T$, setting $T_0'=\pd T$.
Inside $T_0'$ is the set of disjoint parallel longitudes $\Gamma$ that are required to bound disks inside $T'$, so for each $\gamma_i$ we attach a disk $D_i$ with $\pd D_i=\gamma_i$ to $T'_0$ over $\gamma_i$.
Call the result of these attachments $T_1'$.
Adjacent longitudes $\gamma_i$ and $\gamma_j$ bound an annulus $A_{ij}$ in $T_1'$, and $D_i \cup A_{ij}\cup D_j$ is a triangulated 2--sphere that we cone into a 3--disk $D_{ij}$.
For each $ij$, we attach the 3--disk $D_{ij}$ to $T_1'$ over $D_i\cup A_{ij}\cup D_j$ to form the closed solid torus $T'$.

By construction $\pd T'=\pd T$, hence the tori are complementary.
%, so $T$ and $T'$ are complementary.
The longitudinal curves of $T$, the $\gamma_i$, bound triangulated disks in $T'$ thus
% the $\gamma_i$
are meridians of $T'$.
Hence, gluing $T$ and $T'$ over their shared boundary forms a 3--sphere.
We then cone that 3--sphere to produce a 4--disk with an explicit (4,2)--handle structure.
This is the basic structure of Algorithm \ref{alg:build-2-handle}, which we iterate over the combinatorial face blocks of $M_1\subset \pd W$.
Finally, we attach these handles to $W$, forming $W'$.

Let $\mathfrak{B}$ be the collection of combinatorial face blocks of $M_1\subset \pd W$.
Iterating Algorithm \ref{alg:build-2-handle} over $\mathfrak{B}$ yields a collection of (4,2)--handles $\{H_B^2\}_{B\in\mathfrak{B}}$.
The combinatorial face blocks in $\mathfrak{B}$ are disjoint by construction, so we attach our handles in any order.
We form the 4--manifold triangulation $W'$ from $W$ as
\[
	W' = W\cup\{H_B^2\}_{B\in\mathfrak{B}}/\sim,
\]
where $\sim$ is defined by $b\sim \iota(b)$, $\iota$ the identity map $H_B^2\supset B\overset{\iota}{\to} B\subset M_1$.



\begin{algorithm}[h!]
	\caption{Constructing a (4,2)--handle}
	\label{alg:build-2-handle}
	\KwData{A pair $(T,\Gamma)$ where $T$ is a closed solid torus triangulation and $\Gamma$ is a collection of disjoint parallel triangulated longitudes in $\pd T$}
	\KwResult{A 4--disk triangulation $H_T^2$ such that $\pd H_T^2$ is a triangulated 3--sphere with genus 1 Heegard splitting over $\pd T$ and such that $\gamma_i\in\Gamma$ bounds a triangulated disk in $\pd H_T^2\setminus \interior{T}$ for each $i$}
	\Begin{
		First, we construct a complementary solid torus $T'$ with $\pd T=\pd T'$\;
		$T_0'=\pd T$\;
		\ForEach{$\gamma_i\in \Gamma$}{
			$D^2_i=C(\gamma_i)$, the cone of $\gamma_i$\;
		}
		$T_1'=T_0'\cup\{D^2_i\}/\sim$, where $\sim$ is induced by 
		%		defined by $g\sim \iota (g)$, $\iota$ 
		%		the identity
		%		 map
		$\pd D^2_i=\gamma_i\overset{\iota}{\to}\gamma_i\subset T_0'$\;
		\ForEach{adjacent pair of longitudes $\gamma_i,\gamma_j$ from $\Gamma$}{
			$A_{ij}=$ the annulus in $T_1'$ bounded by $\gamma_i$ and $\gamma_j$\;
			$S^2_{ij}=$ the triangulated 2--sphere in $T_1'$ that is precisely $D^2_i\cup A_{ij}\cup D^2_j$\;
			$D^3_{ij}=C(S^2_{ij})$, the cone of $S^2_{ij}$\;
		}
		$T'=T_1'\cup\{D^3_{ij}/\sim\}$, where $\sim$ is induced by
		%		 defined by $s\sim\iota(s)$, $\iota$ the identity map
		$\pd D^3_{ij}=S^2_{ij}\overset{\iota}{\to}S^2_{ij}\subset T_1'$\;
		$S_T^3=T\cup T'/\sim$, where $\sim$ is induced by
		%		 defined by $t\sim\iota(t)$, $\iota$ the identity map 
		$\pd T\overset{\iota}{\to}\pd T'$\;
		$H_T^2=C(S_T^3)$, the cone of $S_T^3$\;
	}
\end{algorithm}

%$B$ possesses the structure of a 3--disk if and only if for some edge $e$ of $B$
%The preimages of the corners of $f(B)$ are parallel longitudes of $B$, and we form a triangulated 2--handle containing $B$ by demanding that these longitudes each bound disks in the 2--handle.

%\begin{figure}[h!]
%	\begin{subfigure}[t]{0.45\textwidth}
%		\caption{Face block analogue: torus.} \label{fig:regular-pl-block-torus}
%	\end{subfigure}
%	\hfill
%	\begin{subfigure}[t]{0.45\textwidth}
%		\caption{Face block analogue: disk.} \label{fig:regular-pl-block-disk}
%	\end{subfigure}
%	
%	\caption{
%		\textbf{A face block analogue $B$ of $M$ and its projection through $f$ in the plane.}
%		$f(B)$ is a convex $n$--gon in the plane for some $n$ that is homeomorphic to either a closed solid torus or a 3--disk.
%%		The preimages of the corners of $f(B)$ are parallel longitudes of $B$, and we form a triangulated 2--handle containing $B$ by demanding that these longitudes each bound disks in the 2--handle.
%	}
%	\label{fig:regular-pl-blocks}
%\end{figure}

The manifold $W'$ is formed by attaching triangulated (4,2)--handles to $W$ over the combinatorial face blocks of $M_1$.
The boundary of $W'$ consists of $M_0 \cup M_1'$, where $M_1'=\pd W'\setminus M_0$ and $M_1'$ is related to $M_1$ via triangulated (3,2)--handle attachments to $M_1$ induced by the triangulated (4,2)--handle attachments to $W$.
We decompose $M_1'$ into primed combinatorial edge or vertex block subtriangulations in a manner similar to that found in Chapter \ref{chapter:smooth}.

Primed combinatorial edge blocks are the result of attaching triangulated (3,2)--handles over annular boundary components of combinatorial edge blocks.
These (3,2)--handles are the triangulated 3-disks $D^3_{ij}$ formed on Line 11 of Algorithm \ref{alg:build-2-handle}, and their attaching regions are the annuli of combinatorial edge blocks that project through $f$ over edge-face region boundaries.

Let $E$ be a combinatorial edge block.
Then $E$ is the product of an orientable surface with an interval, i.e. $E=\Sigma\times\Ilit$, where $\Sigma$ is $S^2$ minus some number of disjoint open balls.
The annuli $\pd \Sigma\times\Ilit$ map through $f$ to edge-face region boundaries, hence these are the attaching sites of (3,2)--handles.
Primed combinatorial edge blocks are constructed by performing all such (3,2)--handle attachments, thus each primed combinatorial edge block is a triangulated $S^2\times\Ilit$.

Differing slightly from Chapter \ref{chapter:smooth}, this exhausts the new cells of $M_1'$ introduced by 2--handle attachment.
This is due to the different shape of combinatorial vertex regions as compared to the vertex regions of Chapter \ref{chapter:smooth}.
In Chapter \ref{chapter:smooth} vertex regions were octagonal and shared edge boundaries with face regions.
Here, combinatorial vertex regions are quadrilateral and share point boundaries with combinatorial face regions.
This point boundary is also shared by a pair of combinatorial edge regions.

Let $x$ be a vertex-face-edge-edge boundary.
Then $f\inv(x)=\{\gamma^i\}$ is a collection of triangulated circles, and each $\gamma^i$ is a longitude of a toroidal combinatorial face block in $M_1$ that projects over the face region whose boundary contains $x$.
Thus, every $\gamma^i$ has been filled by a 2--disc constructed on Line 5 of Algorithm \ref{alg:build-2-handle}.
Each of these new disks has been assigned to two primed combinatorial edge blocks, but we will also assign them to the primed vertex block that contains $\gamma^i$.

This means that each primed combinatorial vertex block is now equivalent to a triangulated (3,2)--handlebody.
Let $V$ be a combinatorial vertex block and $V'$ be $V$ primed.
Considering each new disc in $V'$ to be a flattened (3,2)--handle, we conclude that $V'$ is a (3,2)--handlebody using the argument found in Theorem \ref{thm:primed-block-structure}.
The attaching spheres of (3,2)--handles transversely intersect the belt spheres of the (3,1)--handles at most once, each belt sphere intersects at least one attaching sphere and vice versa, and the boundary of $V'$ is a disjoint collection of 2--spheres, thus $V'$ is a (3,2)--handlebody.

\subsection{3--handles}

We now construct (4,3)--handles to attach over our primed combinatorial edge blocks.
Let $E'$ be such a block.
Then $\pd E'$ is a disjoint pair of triangulated 2--spheres.
We form a 4--disk containing $E'$ in its boundary by a double coning method on $E'$: we first cone the spherical boundary components of $E'$ to form a pair of triangulated 3--disks, glue these 3--disks to $E'$ to form a 3--sphere, then cone the 3--sphere to obtain a 4--disk.
This idea is identical to that found in Section \ref{subsec:smooth-3handles} and is formalized in Algorithm \ref{alg:build-3-handle}.
Finally, we attach (4,3)--handles built using Algorithm \ref{alg:build-3-handle} to $W'$ over primed combinatorial edge blocks.

Let $\mathfrak{E}'$ be the collection of primed combinatorial edge blocks of $M_1'\subset \pd W'$.
Iterating Algorithm \ref{alg:build-3-handle} over $\mathfrak{E}'$ yields a collection of (4,3)--handles $\{H_{E'}^3\}_{E'\in\mathfrak{E}'}$.
The primed combinatorial edge blocks in $\mathfrak{E}'$ intersect only in discs that are also shared by primed combinatorial vertex blocks and these disks are invariant under the (4,3)--handle attachment so we attach our handles in any order.
We form the 4--manifold triangulation $W''$ from $W'$ as
\[
W'' = W'\cup\{H_{E'}^3\}_{E'\in\mathfrak{E}'}/\sim,
\]
where $\sim$ is defined by $e\sim \iota(e)$, $\iota$ the identity map $H_{E'}^3\supset E'\overset{\iota}{\to} E'\subset M_1'$.

\begin{algorithm}[h!]
	\caption{Constructing a 3--handle}
	\label{alg:build-3-handle}
	\KwData{$E'$, a triangulated $S^2\times\Ilit$}
	\KwResult{A 4--disk triangulation $H_{E'}^3$ such that $\pd H_{E'}^3$ is a triangulated 3--sphere containing $E'$ as a subtriangulation}
	\Begin{
		First, we attach 3--disks to $E'$ over its two 2-sphere boundary components\;
		\ForEach{boundary sphere $S^2_i\in \pd E'$}{
			$C(S^2_i)=$ the cone of $S^2_i$\;
			Attach $C(S^2_i)$ to $\pd E'$ over $S^2_i\in \pd E'$\;
		}
		The result of the above attachments is the 3--sphere $S^3_{E'}$\;
		Then $H_{E'}^3=C(S^3_{E'})$\;
	}
\end{algorithm}

The manifold $W''$ is formed by attaching triangulated (4,3)--handles to $W'$ over the primed combinatorial edge blocks of $M_1'$.
The boundary of $W''$ consists of $M_0 \cup M_1''$, where $M_1''=\pd W''\setminus M_0$ and $M_1''$ is related to $M_1'$ via triangulated (3,3)--handle attachments to $M_1'$ induced by the triangulated (4,3)--handle attachments to $W'$.
These (3,3)--handle attachments turn primed combinatorial vertex blocks into double primed combinatorial vertex blocks.
A primed combinatorial vertex block is a (3,2)--handlebody, so a  double primed combinatorial vertex block is a (3,2)--handlebody with each $S^2$ boundary component filled in with a (3,3)--handle, thus each double primed combinatorial vertex block is a triangulated $S^3$.

\subsection{4--handles}

We now construct (4,4)--handles to attach over our double primed combinatorial vertex blocks.
Let $V''$ be such a block.
Then $V''$ is a triangulated $S^3$, so a (4,4)--handle structure that can be attached over $V''$ is constructed by coning $V''$.
These handles are attached to $W''$ to form a triangulated 4--manifold whose only boundary component is $M_0$.

Let $\mathfrak{V}''$ be the collection of double primed combinatorial vertex blocks of $M_1''\subset \pd W''$.
Coning each element of $\mathfrak{V}''$ yields a collection of (4,4)--handles $\{H_{V''}^4\}_{V''\in\mathfrak{V}''}$.
The double primed combinatorial vertex blocks in $\mathfrak{V}''$ are disjoint, so we attach our handles in any order.
We form the 4--manifold triangulation $W'''$ from $W''$ as
\[
W''' = W''\cup\{H_{V''}^4\}_{V''\in\mathfrak{V}''}/\sim,
\]
where $\sim$ is defined by $v\sim \iota(v)$, $\iota$ the identity map $H_{V''}^4\supset V''\overset{\iota}{\to} V''\subset M_1''$.

The triangulated 4--manifold $W'''$ has only one boundary component: $M_0$.
By construction, $M_0$ is equivalent to the original input 3--manifold triangulation $N$ by subdivision of $N$, hence $W'''$ is a triangulated 4--manifold with boundary $N$, as desired.

