\startchapter{How do you obtain a 4--manifold with a specific boundary?}
\label{chapter:problem}

Given a smooth, closed 3--manifold $M$, there are infinitely many 4--manifolds with boundary $M$.
We do not ensure that the constructed 4--manifold has any properties other than a specified boundary, so our construction ensures easy verification that the constructed 4--manifold's boundary is exactly $M$.
This is done by setting $W=M\times \Ilit$, so $W$ has boundary 
\[
	\pd W = (M\times\{0\}) \cup (M\times\{1\}) = M_0 \cup M_1.
\]
We then attach handles to the boundary of $W$ away from $M_0$ until only $M_0$ remains.

The concept of a stratified handle attachment needs some explanation.
First, we define attachment of topological spaces, and use that language to define handle attachment.

\begin{defn}[Attachment]
	Let $X$ and $Y$ be topological spaces, $A\subset X$ a subspace, and $f:A\to Y$ a continuous map.
	We define a relation $\sim$ by putting $f(x)\sim x$ for every $x$ in $A$.
	Denote the quotient space $X\sqcup Y/\sim$ by $X\cup_f Y$.
	We call the map $f$ the \emph{attaching map}.  
	We say that $X$ is \emph{attached} or \emph{glued} to $Y$ over $A$.
	A space obtained through attachment is called an \emph{adjunction space} or \emph{attachment space}.
	
	Alternatively, we let $A$ be a topological space and let $i_X:A\to X$, $i_Y:A\to Y$ be inclusions.
	Here, the adjunction is formed by taking $i_X(a)\sim i_Y(a)$ for every $a\in A$ and we denote the adjunction space by $X\cup_A Y$.
\end{defn}

\begin{defn}[Handle]
	\label{def:handle}
	Take $n=\lambda+\mu$ and $M$ a smooth $n$--manifold with nonempty boundary $\pd M$.
	Let $D^\lambda$ be the closed $\lambda$--disk and put $H^\lambda = D^\lambda\times D^\mu$.
	Let $\varphi:\pd D^\lambda\times D^\mu\to\pd M$ be an embedding and an attaching map between $M$ and $H^\lambda$.
	The attached space $H^\lambda$ is an \emph{$n$--dimensional $\lambda$--handle}, and $M\cup_\varphi H^\lambda$ is the result of an $n$--dimensional \emph{$\lambda$--handle attachment}.
\end{defn}

Handle attachment is defined for smooth manifolds, but the resulting attachment space is not a smooth manifold.
Rather, the result is a stratified manifold.
We use the definition from \cite{wein94}.

\begin{defn}[Stratification]
	$X$ is a \emph{filtered space} on a finite partially ordered indexing set $S$ if 
	\begin{enumerate}
		\item there is a closed subset $X_s$ for each $s\in S$,
		\item $s\leq s'$ implies that $X_s\subset X_{s'}$, and
		\item the inclusions $X_s \into X_{s'}$ satisfy the homotopy lifting property.
	\end{enumerate}
	The $X_s$ are the \emph{closed strata} of $X$, and the differences
	$$X_s\setminus \bigcup_{r < s} X_r$$
	are \emph{pure strata}.
	The pure strata are denoted $X^s$.
	The singular declension of the word strata is \emph{stratum}.
	
	A \emph{filtered map} between spaces filtered over the same indexing set is a continuous function $f:X\to Y$ such that $f(X_s)\subset Y_s$, and such a map is \emph{stratified} if $f(X^s) \subset Y^s$.
	This leads to definitions of stratified homotopy, therefore stratified homotopy equivalence.
\end{defn}

Immediate examples of stratified manifolds are manifolds with boundary and manifolds with corners.
The result of a smooth handle attachment is a manifold with corners at $\varphi(\pd D^\lambda \times \pd D^\mu)$, hence a stratified manifold.



