\section{Handles}
\label{section:problem-handles}

The concept of a stratified handle attachment needs some explanation.
First, we define attachment of topological spaces, and use that language to define handle attachment.
We use Gompf \& Stipsicz \cite{GompStip} as our main reference for handles attachment.

\begin{defn}[Attachment]
	Let $X$ and $Y$ be topological spaces, $A\subset X$ a subspace, and $f:A\to Y$ a continuous map.
	We define a relation $\sim$ by putting $f(x)\sim x$ for every $x$ in $A$.
	Denote the quotient space $X\sqcup Y/\sim$ by $X\cup_f Y$.
	We call the map $f$ the \emph{attaching map}.  
	We say that $X$ is \emph{attached} or \emph{glued} to $Y$ over $A$.
	A space obtained through attachment is called an \emph{adjunction space} or \emph{attachment space}.
	
	Alternatively, we let $A$ be a topological space and let $i_X:A\to X$, $i_Y:A\to Y$ be inclusions.
	Here, the adjunction is formed by taking $i_X(a)\sim i_Y(a)$ for every $a\in A$ and we denote the adjunction space by $X\cup_A Y$.
\end{defn}

\begin{defn}[Handle]
	\label{def:handle}
	Take $n=\lambda+\mu$ and $M$ a smooth $n$--manifold with nonempty boundary $\pd M$.
	Let $D^\lambda$ be the closed $\lambda$--disk and put $H^\lambda = D^\lambda\times D^\mu$.
	Let $\varphi:\pd D^\lambda\times D^\mu\to\pd M$ be an embedding and an attaching map between $M$ and $H^\lambda$.
	The attached space $H^\lambda$ is an \emph{$n$--dimensional $\lambda$--handle}, abbreviated \emph{$(n,\lambda)$--handle}, and $M\cup_\varphi H^\lambda$ is the result of an \emph{$n$--dimensional $\lambda$--handle attachment}, abbreviated \emph{$(n,\lambda)$--handle attachment}.

	Let $n=\lambda+\mu$, let $H^\lambda=D^\lambda\times D^\mu$ be a $(n,\lambda)$--handle, and let $\varphi:\pd D^\lambda\times D^\mu\to\pd M$ be an attaching map from $H^\lambda$ to the $n$--manifold $M$.
	The sphere $\pd D^\lambda\times \{0\}$ in $H^\lambda$ is the \emph{attaching sphere} of $H^\lambda$, and the sphere $\{0\}\times \pd D^\mu$ is the \emph{belt sphere} of $H^\lambda$.	
\end{defn}

Handles $H_1$ and $H_2$ attached to a manifold $M$ are extraneous when $(M\cup H_1)\cup H_2\thickapprox M$.
When this happens, we say that the handles \emph{cancel}.
In the proof of Theorem \ref{thm:primed-block-structure} we attach 2--handles with the intention of canceling 1--handles.


\begin{prop}[Proposition 4.2.9 in \cite{GompStip}]
	A $(k-1)$--handle $H^{k-1}$ and a $k$--handle $H^k$ $(1\leq k\leq n)$ can be canceled, provided the attaching sphere of $H^k$ intersects the belt sphere of $H^{k-1}$ transversely in a single point.
\end{prop}

Handle attachment is defined for smooth manifolds, but the resulting attachment space is not a smooth manifold.
Rather, the result is a manifold with corners.
Some other formulations of handle attachment (e.g.\ \cite{GompStip}) implicitly smooth the corners resulting from handle attachment, so in their formulation of handle cancellation the equivalence relation is strong (i.e. $\thickapprox$ is diffeomorphism).
We do not smooth our corners, so we take $\thickapprox$ to be homeomorphism.
A manifold with corners is an example of a \emph{stratified manifold}, introduced in the next section.




