\chapter{Proof for smooth manifolds}
\label{chapter:smooth}

We prove that every smooth, closed, orientable 3--manifold is the boundary of some 4--manifold.
We do so by explicitly constructing such a 4--manifold from a given 3--manifold.
This construction is mirrored in Chapter \ref{chapter:triangulation} where we prove the same for a given closed, orientable 3--manifold triangulation and provide an algorithm.

Let $M$ be a smooth, closed, orientable 3--manifold and take $W=M\times \Ilit$.
Then $W$ is a 4--manifold with boundary
\[
	\pd W = (M\times\{0\}) \cup (M\times\{1\}) = M_0 \cup M_1.
\]
We construct a manifold with only one boundary component from $W$ by attaching 4--dimensional 2--, 3--, and 4--handles to $W$ over the part of its boundary away from $M_0$.
We start by attaching 2--handles to $W$ over $M_1$ to produce a 4--manifold $W'$ with boundary $M_0 \sqcup M_1'$, where $M_1'=\pd W'\setminus M_0$ and is described via surgery on $M_1$.
We then attach 3--handles to $W'$ over $M_1'$ to produce a 4--manifold $W''$ with boundary $M_0\sqcup M_1''$.
As before, $M_1''=\pd W''\setminus M_1$ and $M_1''$ is described via surgery on $M_1'$.
At this point in the construction, $M_1''$ is the disjoint union of a finite number of copies of $S^3$.
We attach 4--handles to $W''$ over $M_1''$ to produce a 4--manifold whose boundary is exactly $M_0$.

Instructions for handle attachment come from defining a projection $f:M_1\to \RR$ that induces a stratification of $M_1\subset\pd W$.

%
% indexed partially by dimension of the pure strata as a submanifold of $M_1$.
% such that each closed stratum $M_1^3$ is a disjoint collection of open submanifolds of $M_1$.
%
We call a closed 3--dimensional stratum of $M_1$ a \emph{block}, and we impose conditions on $f$ to ensure that every block can be classified up to \emph{stratified homeomorphism}.
We say that $X,Y$ are \emph{stratified homeomorphic} if $X,Y$ are stratified spaces and there exists a homeomorphism $f:X\to Y$ such that $f$ and $f\inv$ are each stratified maps.
The blocks of $M_1$ are described below:

{\renewcommand\labelitemi{}
\begin{itemize}
	\item \textbf{Face block:}
		An attachment neighbourhood for a stratified 2--handle.
		Each face block is stratified-homeomorphic to $S^1\times G_n$, the product of the circle with an $n$-gon for some $n$.
	
	\item \textbf{Edge block:}
		A partial attachment neighbourhood for a stratified 3--handle.
		Each edge block is stratified-homeomorphic to one of $D^2\times\Ilit$, $A\times\Ilit$, or $P\times\Ilit$, where $A$ is the annulus $S^1\times\Ilit$ and $P$ is a pair-of-pants surface.
		Attachment of stratified (4,2)--handles over our face blocks ``fill in'' the annular boundary components of edge blocks, forming full attachment neighbourhoods for stratified 3--handles.
		
	\item \textbf{Vertex block:}
		A partial attachment neighbourhood for a stratified 4--handle.
		Each vertex block is homeomorphic to a (3,1)-handlebody of genus at most 3.
		When stratified (4,2)-- and (4,3)--handles are attached to $W$, the genus of these handlebodies are reduced until the remaining boundary of $W$ consists of $M_0$ union a collection of stratified 3--spheres.  The 3--spheres are then coned away.
\end{itemize}
}
 
The remainder of this chapter is spent ensuring that such a stratification can be achieved for any smooth, orientable, closed 3--manifold, detailing how the stratification is induced, proving that the attachment of stratified (4,2)-- and (4,3)--handles has the previously stated effects, and discussing the resulting 4--manifold.

\input{chapters/3/smooth-projection}

\input{chapters/3/decomposing-r2}

\input{chapters/3/stratifying-m}

\input{chapters/3/smoothhandles}

%\input{chapters/3/conclusion}
